---
title: "SNA Physician ERGM"
author: "Sarah Piombo"
date: "5/10/2022"
output:
  html_document: default
  pdf_document: default
  editor_options: 
    chunk_output_type: console
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(igraph)
library(magrittr)
library(tidyverse)
library(ergm)
library(intergraph)
library(texreg)

#Load in data sets
#Attribute data
att_data
att_data <-   att_data$rolelab2 <- as.factor(att_data$rolelab)
#Advice graph dyads
advice_dyad 
#Advice net data frame
advice_data
#Discussion net attribute data
att_data_dis 
att_data_dis <- att_data_dis$rolelab2 <- as.factor(att_data_dis$rolelab)
#Discussion graph dyads
discuss_dyad 
#Discussion net data frame
discuss_data 
#Full Advice net dyads
advice_all


############## Advice Network ############################
# Remove from network those not in the attribute data
# Do not remove for opinion leader identification
#Use Dyad and Attribute data to construct network
advice_graph <-graph_from_data_frame(advice_dyad, vertices = att_data)

############## Full Advice Network #######################
advice_graph_all <-graph_from_data_frame(advice_all)
V(advice_graph_all)$indegree   <- degree(advice_graph_all, mode = "in")
V(advice_graph_all)$outdegree  <- degree(advice_graph_all, mode = "out")
#Return full advice network to data frame, look at highest indegree to find opinion leaders
data_advice_all <-  as_data_frame(advice_graph_all, what = "vertices")

#################### Discussion Network ###################
#Use discussion dyad and attribute data to construct network
discuss_graph <-graph_from_data_frame(discuss_dyad, vertices = att_data_dis)

```


Creating Network object
```{r ERGMS, include = FALSE}
library(texreg)
set.seed(111)

advice_net <-  intergraph::asNetwork(advice_graph)
discussion_net  <-  intergraph::asNetwork(discuss_graph)

summary(advice_net ~ edges + mutual)
summary(discussion_net ~ edges + mutual)

#Check for loops in both networks
E(advice_graph)[which_loop(advice_graph)]
E(discuss_graph)[which_loop(discuss_graph)]


#Running simple ergm with just edge count on advice network
model0 <- ergm(advice_net ~ edges)
summary(model0)

#Add more effects to model - adding reciprocity and gwesp effects
model1 <-  ergm(advice_net ~ edges + 
                  mutual +
                  gwesp(0.1, fixed = T),
                constraints = ~bd(maxout = 7)) 
summary(model1)

#Add nodefactor and nodematching effects for occupational role and awareness of clinic
advicemod <-  ergm(advice_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwesp(0.1, fixed = T),
                constraints = ~bd(maxout = 7)) 
summary(advicemod)

#Run the same model on the discussion network
discussionmod <-  ergm(discussion_net ~ edges + 
                 nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwesp(0.1, fixed = T),
                constraints = ~bd(maxout = 7)) 
summary(discussionmod)

#Output 
#screenreg(list( model0, model1, advicemod, discussionmod))
```

Updated for revision #2 with gw*degree terms
```{r gwdegree ergms advice net}
#gwodegree
advicemod_gwo <-  ergm(advice_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwodegree(0.1, fixed=T) +
                  gwesp(0.1, fixed=T),
                constraints = ~bd(maxout = 7),
                control = control.ergm(seed = 111,
                                       MCMLE.maxit = 10,
                                       parallel = 4,
                                       CD.maxit = 10,
                                       MCMC.samplesize = 2000*4,
                                       MCMC.burnin = 25000,
                                       MCMC.interval = 2000*4)) 

summary(advicemod_gwo)
adv <- screenreg(list(advicemod_gwo))


advicemod_gwo2 <-  ergm(advice_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwodegree(0.5, fixed=T) +
                  gwesp(0.5, fixed=T),
                constraints = ~bd(maxout = 7),
                control = control.ergm(seed = 111,
                                       MCMLE.maxit = 10,
                                       parallel = 4,
                                       CD.maxit = 10,
                                       MCMC.samplesize = 2000*4,
                                       MCMC.burnin = 25000,
                                       MCMC.interval = 2000*4)) 

summary(advicemod_gwo2)

#gwidegree
advicemod_gwi <-  ergm(advice_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwidegree(0.1, fixed=T) +
                  gwesp(0.1, fixed=T),
                constraints = ~bd(maxout = 7),
                control = control.ergm(seed = 111,
                                       MCMLE.maxit = 10,
                                       parallel = 4,
                                       CD.maxit = 10,
                                       MCMC.samplesize = 2000*4,
                                       MCMC.burnin = 25000,
                                       MCMC.interval = 2000*4)) 
summary(advicemod_gwi)


#didn't converge
advicemod_gw <-  ergm(advice_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwodegree(0.5, fixed=T)+
                  gwidegree(0.5, fixed=T)+
                  gwesp(0.1, fixed=T),
                constraints = ~bd(maxout = 7),
                control = control.ergm(seed = 111,
                                       MCMLE.maxit = 10,
                                       parallel = 4,
                                       CD.maxit = 10
                                       #MCMC.samplesize = 2000*4,
                                       #MCMC.burnin = 25000,
                                       #MCMC.interval = 2000*4
                                       )) 
summary(advicemod_gw)

gws <- screenreg(list(advicemod_gwo, advicemod_gwi))
gws
write.table(gws, "adgw.txt")


mcmc.diagnostics(advicemod_gwi)
adgwi_gof <- gof(advicemod_gwi)
plot(adgwi_gof)


mcmc.diagnostics(advicemod_gwo)
adgwgof = gof(advicemod_gwo, GOF = ~model)
adgwgof
adgw_gof <- gof(advicemod_gwo)
plot(adgw_gof)

library(coda)
adsamplegwo <- advicemod_gwo$sample
coda::gelman.diag(adsamplegwo)

adsamplegwi <- advicemod_gwi$sample
coda::gelman.diag(adsamplegwi)

```

Gw*degree terms for discussion network
```{r gwdegree ergms discuss net}

#GWodegree 
discussmod_gwo <-  ergm(discussion_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwodegree(0.1, fixed=T) +
                  gwesp(0.1, fixed=T),
                constraints = ~bd(maxout = 7),
                control = control.ergm(seed = 111,
                                       MCMLE.maxit = 10,
                                       parallel = 4,
                                       CD.maxit = 10,
                                       MCMC.samplesize = 2000*4,
                                       MCMC.burnin = 25000,
                                       MCMC.interval = 2000*4))
                 

summary(discussmod_gwo)

#Gwidegree
discussmod_gwi <-  ergm(discussion_net ~ edges + 
                  nodefactor("rolelab", levels=-3) +
                  nodematch("rolelab") + 
                  nodefactor("lifeaware") +
                  nodefactor("liferefer") +
                  nodematch("lifeaware") +
                  nodematch("liferefer") +
                  mutual +
                  gwidegree(0.1, fixed=T) +
                  gwesp(0.1, fixed=T),
                constraints = ~bd(maxout = 7),
                control = control.ergm(seed = 111,
                                       MCMLE.maxit = 10,
                                       parallel = 4,
                                       CD.maxit = 10)) 
summary(discussmod_gwi)

dissgws <- screenreg(list(discussmod_gwo, discussmod_gwi))
dissgws
write.table(dissgws, "dissgw.txt")

disssamplegwo <- discussmod_gwo$sample
coda::gelman.diag(disssamplegwo)

#MCMC Diagnostics
mcmc.diagnostics(discussmod_gwo)
disgwogof = gof(discussmod_gwo, GOF = ~model)
disgwogof
disgwo_gof <- gof(discussmod_gwo)
par(mfrow=c(2,2))
plot(disgwo_gof)


ergmans <- (list(advicemod_gwo, discussmod_gwo))
htmlreg(ergmans, custom.model.names = c("Advice", "Discussion"), caption.above = TRUE, caption = "ERGMS", digits = 2, single.row = T, center =T, file = "/Users/sarahpiombo/Documents/R/Projects/SNA Physicians/output_data/ergm_final.html")
```

Model Fit
Model 3 is the Advice model and Model 4 is the Discussion Model
Included the diagnostics and goodness of fit for the two models
```{r Model fit}
screenreg(list(advicemod, discussionmod))

#mcmc.diagnostics(advicemod)
adgof = gof(advicemod, GOF = ~model)
adgof
advice_gof <- gof(advicemod)
plot(advice_gof)

#mcmc.diagnostics(discussionmod)
disgof = gof(discussionmod, GOF = ~model)
disgof
discussion_gof <- gof(discussionmod)
plot(discussion_gof)

```

Logistic Regression for factors associated with surivorship clinic referral
```{r Logistic Regression}
att_data <- merge(advice_data, discuss_data, by= c("name"), all.x = T, all.y = T)
discuss_data <- mutate(discuss_data, rolelabel = as.factor(rolelable))

#Advice Network
model_ad1 <- advice_data %>% 
  glm(liferefer ~ refer_expo + betweeness + relevel(rolelab2, ref = 3), data = ., family =binomial(link = logit))
summary(model_ad1)

model_ad2 <- advice_data %>% 
  glm(lifeaware ~ refer_expo + betweeness + rolelable, data = ., family =binomial(link=logit))
  summary(model_ad2)

#Discussion Network Models - betweenness is sig.
model_dis1 <- discuss_data %>% 
  glm(liferefer ~ refer_expo +  betweeness + relevel(rolelable, ref = "Nurse")  , data = ., family =binomial(link=logit))
summary(model_dis1)

model_dis2 <- discuss_data %>% 
  glm(lifeaware ~  refer_expo, data = ., family =binomial())
  summary(model_dis2)

## Revised Model for Revision
summary(discuss_data$betweeness)
discuss_data$bet100 <- discuss_data$betweeness*100 #betweenness needed to be multiplied
summary(discuss_data$bet100)
model_dis3 <- discuss_data%>% 
  glm(liferefer ~   refer_expo + bet100 + relevel(rolelabel, ref = "Nurse")  , data = ., family =binomial(link=logit))
summary(model_dis3)
disnetmod_final <- model_dis3 %>% 
  tidy(.) %>% 
  kable(., digits = c(0,3,3,3,3))
disnetmod_final

```

Network graphs: regular ones and the ones sized by degree
```{r Graphing the  Networks}
advice_network <- cbind(
  size    = vcount(advice_graph),
  nedges  = ecount(advice_graph),
  density = edge_density(advice_graph),
  recip   = reciprocity(advice_graph),
  centr   = centr_betw(advice_graph)$centralization,
  pathLen = mean_distance(advice_graph)
  )

#Advice network filtered for people with attribute data
col_role <- c("lightslateblue", "tomato", "palegreen3", "orange2", "palegoldenrod")
V(advice_graph)$color <- col_role[V(advice_graph)$rolelab]

shape2 <-   c("circle", "square")
V(advice_graph)$shape <- shape2[V(advice_graph)$liferefer+1]

#Checking betweeness cutoff for labels
betlab <- betweenness(advice_graph)
betlab <- ifelse(betlab>150, V(advice_graph)$name, NA)

#Plotting the advice network
plot(
  advice_graph,
  vertex.size     = degree(advice_graph)/2 +2 ,
  vertex.label    = V(advice_graph)$betlab,
  vertex.label.cex = 0.7,
  vertex.label.color = c("gray44"),
  vertex.label.family="Helvetica",
  vertex.label.dist=0.2,
  layout= layout_with_fr,
  edge.arrow.size = .25,
  vertex.color = V(advice_graph)$color,
  vertex.shape = V(advice_graph)$shape)
  title(main = "Advice Network with Indegree" )
  legend("bottomleft", legend =c("Physician", "NP/PA", "Clinic Nurse", "Social Worker", "Scheduler/other"), pch=21,
  col="#777777", pt.bg=col_role, pt.cex=1, cex=1, bty="n", ncol=1)

dev.off()

#Advice network with everyone (includes people who were nominated but did not participate)
plot(
  advice_graph_all,
  vertex.size     = degree(advice_graph_all)/2 +2 ,
  layout = layout_with_kk,
  vertex.label    = NA,
  edge.arrow.size = .25,
  vertex.color = "tomato"
  )
  title(main = "Advice Network with Everyone" )
dev.off()


#Discssion Network
discussion_network <- cbind(
  size    = vcount(discuss_graph),
  nedges  = ecount(discuss_graph),
  density = edge_density(discuss_graph),
  recip   = reciprocity(discuss_graph),
  centr   = centr_betw(discuss_graph)$centralization,
  pathLen = mean_distance(discuss_graph)
  ) %>% 
  print()

#Shape and color for the discussion network
shape2 <-   c("circle", "square")
V(discuss_graph)$shape <- shape2[V(discuss_graph)$liferefer+1]

col_role2 <- c("lightslateblue", "tomato", "palegreen3", "orange2",  "palegoldenrod")
V(discuss_graph)$color <- col_role2[V(discuss_graph)$rolelab]

#Plotting discussion network
plot(
  discuss_graph, 
  vertex.size     = degree(discuss_graph)/2 +2 ,
  vertex.label    = NA,
  layout = layout_nicely,
  edge.arrow.size = .25,
  vertex.color = V(discuss_graph)$color,
  vertex.shape = V(discuss_graph)$shape
  )
title(main = "Discussion Network with Indegree")
legend("bottomleft", legend =c("Physician", "NP/PA", "Nurse", "Social Worker", "Scheduler/other"), pch=21,
  col="#777777", pt.bg=col_role2, pt.cex=1, cex=1, bty="n", ncol=1)
dev.off()

#Plotting discussion network with all nodes the same size
plot(
  discuss_graph,
  vertex.size     = 5,
  vertex.label    = NA,
  layout = layout_with_kk,
  edge.arrow.size = .25,
  vertex.color = col_role2
  ) 
title(main = "Discussion Network") 
legend("bottomleft", legend =c("Physician", "NP/PA", "Nurse", "Social Worker", "Scheduler/other"), pch=21,
  col="#777777", pt.bg=col_role2, pt.cex=1, cex=.9, bty="n", ncol=1)
dev.off()

#LABELING NODES WITH ONLY HIGH BETWEENNESS CENTRALITY
betlab <- betweenness(advice_graph)
betlab <- ifelse(betlab>150, V(advice_graph)$name, NA)
V(advice_graph)$betlab <- betlab

betlab2 <- betweenness(discuss_graph)
betlab2 <- ifelse(betlab2>250, V(discuss_graph)$name, NA)

#RESCALING LAYOUT
l <- layout_nicely(advice_graph)
l <- norm_coords(l, ymin=-1, ymax=1, xmin=-1, xmax=1)
  rescale = F, layout=l*0.8
  
#CREATING LABELS FOR HIGH BETWEENNESS INDIVIDUALS
bet <- ifelse(betweenness(advice_graph) > 200, 1, ifelse(betweenness(advice_graph)>170, 2,
       ifelse(betweenness(advice_graph)>160, 3, NA)))
bet2 <- ifelse(betweenness(discuss_graph) > 370, 4, ifelse(betweenness(discuss_graph)>363, 5,
        ifelse(betweenness(discuss_graph)>360, 1, NA)))

#Two panel plot of advice and discussion networks
#This is the final figure for publication
png(filename= "", 
    width=12, height=9,
    units="in", res=300, pointsize=11)
par(mfrow=c(1,2))
plot(
  advice_graph,
  vertex.size     = (degree(advice_graph)/2 +5),
  vertex.label = bet, 
  vertex.label.cex = 1,
  vertex.label.color = c("black"),
  vertex.label.family="Arial",
  vertex.label.font =2,
  layout = layout_nicely,
  edge.arrow.size = .25,
  edge.curved = (0.5),
  vertex.color = V(advice_graph)$color,
  vertex.shape = V(advice_graph)$shape)
  title(main = "Advice Network" )
  legend("bottomleft", legend =c("Physician", "Nurse Practioner/Physician Assistant", "Clinic Nurse", "Social Worker", "Scheduler/other"), 
  pch=21,
  col="#777777", pt.bg=col_role, 
  pt.cex=1, cex=1, 
  bty="n", ncol=1)
  
  plot(
  discuss_graph, 
  vertex.size     = (degree(discuss_graph)/2 +5),
  vertex.label = bet2, 
  vertex.label.cex = 1,
  vertex.label.color = c("black"),
  vertex.label.family="Arial",
  vertex.label.font =2,
  #vertex.label.dist=1,
  layout = layout_nicely,
  edge.arrow.size = .25,
  edge.curved = (0.5),
  vertex.color = V(discuss_graph)$color,
  vertex.shape = V(discuss_graph)$shape

  )
title(main = "Discussion Network")

dev.off()

```
